Anxiety_vis

### 2023-04-21 Anxiety_Vis.Rmd
deleting all my hard work :/

```{r}
#Plot the Anxiety Mean for Full Sample
ggplot(data=Mothership_Mean_CUXOS,aes(x=TxDay,y=mean_CUXOS))+
  geom_line(size=1,color="red")+
  geom_point(color="red")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  ggtitle("Mean Anxiety Severity During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
  scale_y_continuous(name="Anxiety Severity",limits=c(20,40,by=5))+
  theme(panel.background=NULL) +
  geom_vline(xintercept = 5, color = "#BB9D00",alpha =.5)+
  geom_vline(xintercept = 8, color = "orange",alpha =.5)+
  geom_vline(xintercept = 13, color = "red",alpha =.5)+
  annotate("text", x = 5, y = 39, label = "Q1") +
  annotate("text", x = 8, y = 39, label = "Mean") +
  annotate("text", x = 13, y = 39, label = "Q3")

>>>>

```{r}
#Plot the Anxiety Mean for Full Sample
ggplot(data=Mothership_Mean_CUXOS,aes(x=TxDay,y=mean_CUXOS))+
  geom_line(size=1,color="red")+
  geom_point(color="red")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  ggtitle("Mean Anxiety Severity During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
  scale_y_continuous(name="Anxiety Severity",limits=c(20,40,by=5))+
  theme(panel.background=NULL)
